# Conduct: Skillbuilding and calculating scores {#conduct}


TODO: Intro that also distinguishes: 

- http://ohi-science.org/data-science-training/
- https://ohi-science.org/manual/ 

```{r setup-conduct}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

## load libraries
library(tidyverse)
library(glue)
library(gt)

## read in data
sched_sheet <- read_csv("schedule_sheet.csv") 
```

```{r conduct-table}
## wrangle
sched <- sched_sheet %>%
  mutate(Action = case_when(!is.na(Link1) ~ glue("[{Action}]({Link1})"), 
                            is.na(Link1) ~ Action)) %>%
  filter(Chapter == "Conduct") %>%
  mutate(Section = row_number()) %>%
  # TODO mutate(Section = glue Rmd header anchor link
  select(Section, Topic, Action, Minutes)

## create gt table
source("create_ohi_gt.R")
sub_gt <- create_ohi_gt(sched)  %>%
  tab_header(title = "OHI Onboarding Roadmap: Conduct")

sub_gt

```

## Intro to the OHI Toolbox

**`r sched$Action[1]`.**

This video walks through Chapter 8 of the [OHI Toolbox-training](http://ohi-science.org/toolbox-training/). It was recorded as a live-demo in 2018 to introduce OHI+ Kenya and OHI+ Tanzania teams to the Toolbox Workflow. Screensharing from RStudio and GitHub, it repeats the basic Toolbox workflow several times, using demo data, updated data, and updated models.

Additional resources: 

- <https://github.com/ohi-science/toolbox-demo>
  <!--- TODO add the ao_poverty to the scenario_years, it's described in the video ~1:40h for Chapter 8 (Also an idea to clarify in Chapter 9 about deleting a goal) --->
- <http://ohi-science.org/manual>
<!---

Is presented as a stand-alone
Walks through prerequesites requieed: R,/RStudio/GH, and fork/clone download
--->

## Intro to open data science

**`r sched$Action[2]`.**

## Create your OHI+ repo

**`r sched$Action[3]`.**

## Toolbox overview

**`r sched$Action[4]`.**

## Etc as I fine-tune


## Further learning {#conduct-further}

- Frazier et al Gapfilling


The [OHI Manual](https://ohi-science.org/manual/) is a good reference document as well. (A bit of history: this is how the whole ohi-science.org website started; this was originally a PDF created from a Word Doc that we would email to interested groups).
