--- 
title: "Ocean Health Index Onboarding"
author: "OHI Team"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is onboarding learning roadmap to lead Ocean Health Index assessments"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


# Welcome {#welcome}

Hello! This book aims to help you get "on board" with Ocean Health Index (OHI) methods and practices as you lead your own independent OHI assessment (OHI+). It helps orient you to OHI training resources, with chapters organized in the same way as we introduce [OHI+ assessments](https://ohi-science.org/projects/ohi-plus/) at <http://ohi-science.org>.


The **OHI Onboarding Roadmap** below outlines 20 hours of training resources that you can watch and read as self-paced learning as your time allows. The table provides quick links to videos and articles, and each book chapter provides further details and resources.

<br>

```{r setup-full-table}
## load libraries
library(tidyverse)
library(gt)

## read in data
sched_sheet <- read_csv("schedule_sheet.csv") 
load_from_gsheets = FALSE

if(load_from_gsheets == TRUE) {
  library(googlesheets4) # install.packages("googlesheets4")
  ## read sheet from shared OHI Google Folder
  sched_sheet <- read_sheet("https://docs.google.com/spreadsheets/d/1JCY6DIeNs1NjouehLYm32Ulq2XCOCaWx5vBpuhsgKbg/edit#gid=0")
  ## save local copy, overwrite anytime read from googlesheets4
  write_csv(sched_sheet, "schedule_sheet.csv")
}

```

```{r full-table}
## wrangle
sched <- sched_sheet %>%
  mutate(Chapter = str_to_title(Chapter)) %>%
  select(Chapter, Topic, Action, Minutes, Status) %>% 
  filter(!is.na(Chapter))%>%
  group_by(Chapter)

## create gt table
source("create_ohi_gt.R") # making & loading as a package seems overkill
sched_gt <- create_ohi_gt(sched)

sched_gt

```

 and [OHI-Science YouTube](https://www.youtube.com/channel/UCWKfLAbARCmxmzqyaF-ROdg/videos).



<!---
We suggest looking through each chapter of this book at the resources available, and creating a learning plan for your timeline. Below is a suggested example. *upcoming*




Orient to the book, the websites, “github repos”
Ohi-science.org incl ohi-global, OHI+ websites.
Oceanhealthindex.org? Website
books
--->

