--- 
title: "Ocean Health Index Onboarding"
author: "OHI Team"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is onboarding learning roadmap to lead Ocean Health Index assessments"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


# Welcome {#welcome}

Hello! This book aims to help you get "on board" with Ocean Health Index (OHI) methods and practices as you lead your own independent OHI assessment (OHI+). 

It helps orient you to OHI resources and suggests an order that you read and watch them. Book chapters are organized in the same way as we introduce [OHI+ assessments](https://ohi-science.org/projects/ohi-plus/): Learn, Plan, Conduct, and Inform. Most resources are hosted at <http://ohi-science.org> and [OHI-Science YouTube](https://www.youtube.com/channel/UCWKfLAbARCmxmzqyaF-ROdg/videos).

Below is the OHI Onboarding Roadmap with quick links to each lesson; review specific Chapters for more details.


```{r}
library(tidyverse)
library(googlesheets4) # install.packages("googlesheets4")
library(gt) # install.packages("gt")
library(janitor) # install.packages("janitor")

## read sheet from shared OHI Google Folder
# sched_sheet <- read_sheet("https://docs.google.com/spreadsheets/d/1JCY6DIeNs1NjouehLYm32Ulq2XCOCaWx5vBpuhsgKbg/edit#gid=0")
# 
# # save local copy, overwrite anytime read from googlesheets4
# write_csv(sched_sheet, "schedule_sheet.csv")

sched_sheet <- read_csv("schedule_sheet.csv")

```

```{r}
sched <- sched_sheet %>%
  janitor::clean_names(case = "title") %>%
  mutate(Chapter = str_to_title(Chapter)) %>%
  # mutate(Action = str_replace(Action, "watch", "view")) %>%
  select(Chapter, Topic, Action, Minutes, Status) %>% # add links
  filter(!is.na(Chapter))

sched_gt <- sched %>%
  group_by(Chapter) %>%
  gt() %>%
  tab_header(title = "OHI Onboarding Roadmap") %>%
  tab_style(cell_text(align = "left", weight = "bold"), locations = cells_title()) %>%
  tab_style(cell_fill("grey97"), locations = cells_row_groups()) %>%
  tab_style(cell_fill("grey97"), 
            locations = cells_column_labels(columns = gt::everything())) %>% # troubleshooted for hours: jihongzhang.org/post/study-notes-gt-package-and-format-table/
  tab_style(cell_text(weight = "bold"), 
            locations = cells_column_labels(columns = gt::everything())) %>%
  tab_style(cell_fill("white"), locations = cells_body()) %>%
  tab_style(cell_text(indent = pct(1.5)), locations = cells_body()) %>%
  tab_style(cell_text(weight = "bold"), locations = cells_row_groups()) 


sched_gt

```





<!---
We suggest looking through each chapter of this book at the resources available, and creating a learning plan for your timeline. Below is a suggested example. *upcoming*




Orient to the book, the websites, “github repos”
Ohi-science.org incl ohi-global, OHI+ websites.
Oceanhealthindex.org? Website
books
--->

<!---

## Suggested Agenda

| Time        |                                                        Day 1|                                          Day 2|
|:------------|------------------------------------------------------------:|----------------------------------------------:|
| 9-10:30     |  [Motivation](#overview), [R & RStudio, RMarkdown](#rstudio)|              [Charts with `ggplot2`](#ggplot2)|
| break       |                                                             |                                               |
| 11-12:30    |                                   [Intro to GitHub](#github)|  [`dplyr` & Pivot Tables](#dplyr-pivot-tables)|
| lunch       |                                                             |                                               |
| 13:00-14:30 |                          [Importing data: `readxl`](#readxl)|          [`dplyr` & VLOOKUPs](#dplyr-vlookups)|

--->
