--- 
title: "Ocean Health Index Onboarding"
author: "OHI Team"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is onboarding learning roadmap to lead Ocean Health Index assessments"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


# Welcome {#welcome}

Hello! This book aims to help you get "on board" with Ocean Health Index (OHI) methods and practices as you lead your own independent OHI assessment (OHI+). It helps orient you to OHI training resources, with chapters organized in the same way as we introduce [OHI+ assessments](https://ohi-science.org/projects/ohi-plus/) at <http://ohi-science.org>.

The OHI process has 4 steps: Learn, Plan, Conduct, and Inform. These steps are are overlapping and iterative: as you plan your assessment you will continue to learn, as you conduct your assessment you will need to modify your plan and keep team members and stakeholders informed. You'll also find Appendix 1 provides details about the OHI Global Assessment, which is repeated annually each year with less time and resources because of the structure we have created.

## Onboarding Roadmap

The **OHI Onboarding Roadmap** below outlines 15 hours of training — resources that you can asynchronously watch and read as self-paced learning as your time allows. Please visit each chapter in this book, which provides further details and resources.

<br>

```{r setup-full-table}
## load libraries
library(tidyverse)
library(glue)
library(gt)

## read in data
sched_sheet <- read_csv("schedule_sheet.csv") 
load_from_gsheets = TRUE

if(load_from_gsheets == TRUE) {
  library(googlesheets4) # install.packages("googlesheets4")
  ## read sheet from shared OHI Google Folder
  sched_sheet <- read_sheet("https://docs.google.com/spreadsheets/d/1JCY6DIeNs1NjouehLYm32Ulq2XCOCaWx5vBpuhsgKbg/edit#gid=0")
  ## save local copy, overwrite anytime read from googlesheets4
  write_csv(sched_sheet, "schedule_sheet.csv")
}

```

```{r full-table}
## wrangle
sched <- sched_sheet %>%
  mutate(Action = case_when(!is.na(Link1) ~ glue("[{Action}]({Link1})"), 
                            is.na(Link1) ~ Action)) %>%
  select(Chapter, Topic, Action, Minutes) %>% 
  filter(!is.na(Chapter), Chapter != "Revisit") %>%
  filter(!is.na(Chapter), Chapter != "OMIT") %>%
  group_by(Chapter)

## create gt table
source("create_ohi_gt.R") # making & loading as a package seems overkill
sched_gt <- create_ohi_gt(sched)

sched_gt

```

## Citation policy

Please see our [citation policy](https://ohi-science.org/citation-policy/) to cite the Ocean Health Index and assessment resources. 

## OHI Quick Links

- https://ohi-science.org/learn/
- https://ohi-science.org/plan/
- https://ohi-science.org/goals
-  [OHI-Science YouTube](https://www.youtube.com/channel/UCWKfLAbARCmxmzqyaF-ROdg/videos).
- <https://ohi-science.org/resources/forum/>
- Other training resources are linked from the [ohi-science.org training page](https://ohi-science.org/training/). 


<!---
We suggest looking through each chapter of this book at the resources available, and creating a learning plan for your timeline. Below is a suggested example. *upcoming*




Orient to the book, the websites, “github repos”
Ohi-science.org incl ohi-global, OHI+ websites.
Oceanhealthindex.org? Website
books
--->

