# Learn: What is the OHI? {#learn}

There is a lot to learn about the Ocean Health Index framework to best prepare you for leading your own OHI+ assessment. We recommend reading and watching the following, to start with a broad overview and then get deeper into different aspects of OHI. Then, continue to come back to review these materials throughout your assessment. 

```{r setup-learn}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

## load libraries
library(tidyverse)
library(glue)
library(gt)

## read in data
sched_sheet <- read_csv("schedule_sheet.csv") 
```

```{r learn-table}
## wrangle
sched <- sched_sheet %>%
  mutate(Action = case_when(!is.na(Link1) ~ glue("[{Action}]({Link1})"), 
                            is.na(Link1) ~ Action)) %>%
  filter(Chapter == "Learn") %>%
  mutate(Section = row_number()) %>%
  # TODO mutate(Section = glue Rmd header anchor link
  select(Section, Topic, Action, Minutes)

## create gt table
source("create_ohi_gt.R")
sub_gt <- create_ohi_gt(sched)  %>%
  tab_header(title = "OHI Onboarding Roadmap: Learn")

sub_gt

```

## Overview and welcome

**`r sched$Action[1]`.**

What to expect. 

This follows [toolbox-training Chapter 2](https://ohi-science.org/toolbox-training/intro.html).

## Intro to OHI

**`r sched$Action[2]`.**

**Drivers and implications of change in global ocean health** is a webinar given by OHI founding members Dr. Ben Halpern and Dr. Steve Katona. [more paragraph(s): It covers xyz, you will learn xyz.]

## Intro to OHI+

**`r sched$Action[3]`**

**Transforming how we approach marine science for management** is a webinar given by OHI+ leads Dr. Julia Lowndes and Eric Pacheco. This provides an overview of what's involved with leading an OHI assessment and what to think about as you begin. [more]


## Intro to OHI Goals

**`r sched$Action[4]`**

**Intro to OHI Goals: A deep dive into global design** is a presentation developed by OHI senior analyst Melanie Frazier [more]

## Best practices

**`r sched$Action[5]`**

**Best practices for assessing ocean health in multiple contexts using tailorable frameworks** is an open-access publication by Lowndes et al, 2015. 

Lowndes JSS, Pacheco EJ, Best BD, Scarborough C, Longo C, Katona SK, Halpern BS. 2015. Best practices for assessing ocean health in multiple contexts using tailorable frameworks. *PeerJ* 3:e1503 <https://doi.org/10.7717/peerj.1503> 


## Further learning {#learn-further}

1. [**What makes OHI stand out in the sea of environmental indicators?**](https://ohi-science.org/news/goal-forward-approach)
  - It is a goal-forward approach
1. [Three Lessons for Using the Global Ocean Health Index to Assess Local Oceans](https://ohi-science.org/news/three-lessons-global). (Seifert 2019). 
  - "Three interrelated things seem to stand out: include the right people from the start, fit the framework to the place, and align with existing regional efforts."
  

<!---
- https://ohi-science.org/learn/
- https://ohi-science.org/plan/
- https://ohi-science.org/goals
--->

