# Learn: What is the Ocean Health Index? {#learn}

The Ocean Health Index (OHI) is a [goal forward approach](https://ohi-science.org/news/goal-forward-approach)

There is a lot to learn about the Ocean Health Index framework in order to best prepare you for leading your own assessment. We recommend reading and watching the following, to start with a broad overview and then get deeper into different aspects of OHI. Then, continue to come back to review these materials throughout your assessment. 

```{r setup-learn}
## load libraries
library(tidyverse)
library(gt)

## read in data
sched_sheet <- read_csv("schedule_sheet.csv") 
```

```{r learn-table}
## wrangle
sched <- sched_sheet %>%
  mutate(Chapter = str_to_title(Chapter)) %>%
  select(Chapter, Topic, Action, Minutes) %>% 
  filter(!is.na(Chapter))%>%
  group_by(Chapter) %>%
  filter(Chapter == "Learn")

## create gt table
source("create_ohi_gt.R")
learn_gt <- create_ohi_gt(sched)

learn_gt

```




- [**Title**](link) - (slides). Introduction to OHI framework and global assessments by Ben Halpern and Steve Katona.
- Halpern & Katona etc


## Further reading {#ohi-further-reading}

- [**What makes OHI stand out in the sea of environmental indicators?**](https://ohi-science.org/news/goal-forward-approach)
- https://ohi-science.org/learn/
- https://ohi-science.org/plan/
- https://ohi-science.org/goals

