# Plan: The OHI Process {#process}

The OHI follows a very structured approach. There are core elements and approaches that you will not change and tailorable elements so that you can fit your needs. It's important to begin your OHI+ assessment in a way that organized and collaborative, expecting that team members might change and that methods might be revisited. Thus, working like a team and building in resilience from the beginning is critical: focus on documentation and sharing and avoid having only one person who knows or can do something. 

```{r setup-plan}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

## load libraries
library(tidyverse)
library(glue)
library(gt)

## read in data
sched_sheet <- read_csv("schedule_sheet.csv") 
```

```{r plan-table}
## wrangle
sched <- sched_sheet %>%
  mutate(Action = case_when(!is.na(Link1) ~ glue("[{Action}]({Link1})"), 
                            is.na(Link1) ~ Action)) %>%
  filter(Chapter == "Plan") %>%
  mutate(Section = row_number()) %>%
  # TODO mutate(Section = glue Rmd header anchor link
  select(Section, Topic, Action, Minutes)

## create gt table
source("create_ohi_gt.R")
sub_gt <- create_ohi_gt(sched) %>%
  tab_header(title = "OHI Onboarding Roadmap: Plan")

sub_gt

```

## Overview of Resources

**`r sched$Action[1]`.**

## Planning your assessment

**`r sched$Action[2]`.**

## Gathering and organizing data

**`r sched$Action[3]`.**

## Better science in less time

**`r sched$Action[4]`.**

**Our path to better science in less time using open data science tools** (Lowndes et al 2017, Nature Ecology & Evolution). This will provide an overview of how we use the OHI Toolbox and why.


## Overview of the OHI Toolbox software

**`r sched$Action[5]`.**



## Further learning {#plan-further}

1.  Read [Operationalizing better science in less time](https://docs.google.com/presentation/d/1OHe4C2B9cGnT9niSguXwsWiK0M2sDsdeNjTOLWAgBX4/edit?usp=sharing). These slides describe how OHI is about environmental assessments, but it's also about open data science and empowerment, resilience, and inclusion and the importance of teamwork. 
1. [On Building Transparency and Trust for Healthy New England Seas](https://ohi-science.org/news/transparent-trust-new-england-seas)
1. [Open data science for marine management](https://ohi-science.org/news/ohi-and-open-data-science) (blog)
1. [What does scientific reproducibility look like?](https://ohi-science.org/news/scientific-reproducibility-with-fellows) (blog)
1. [The OHI Toolbox is useful far beyond ocean management](https://ohi-science.org/news/what-is-the-ohi-toolbox) (blog)


<!---
1. Teams. *TODO*. team roles, seaside chats, have meeting notes, write down decisions, etc. OHI+ examples Onboarding transparency, stakeholder engagement, teams open data science

This process is summarized on the [ohi-science.org OHI+ page](https://ohi-science.org/projects/ohi-plus/).

--->

